Revisiting the hydrodynamic modulation of short waves by longer waves

### 2024-09-28 paper/paper.tex
Tiny edits

\begin{equation}
\label{eq:wave_action}
\dfrac{\partial N}{\partial t}
+ \dfrac{\partial}{\partial x} \left[\left(C_g + U\right)N\right]
= 0
\end{equation}
where $N$ is the action density, and $C_g = 1/2\sqrt{g/k}$ is the group speed
in deep water.
Although the absence of wave growth and dissipation is not generally realistic
in the open ocean, it is a helpful approximation here to isolate the effects
of hydrodynamic modulation solely due to the motion of the long waves.

@@

\backsection[Data availability statement]{
  The code to run the numerical simulations and generate the figures in this
  paper is available at \url{https://github.com/wavesgroup/wave-modulation-paper}.
  The numerical model is available as a standalone package at
  \url{https://github.com/wavesgroup/2wave}.
  %See JFM's \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/journal-policies/research-transparency}{research transparency policy} for more information
}

>>>>

\begin{equation}
\label{eq:wave_action}
\dfrac{\partial N}{\partial t}
+ \dfrac{\partial}{\partial x} \left[\left(C_g + U\right)N\right]
= 0
\end{equation}
where $N$ is the action density, and $C_g = 1/2\sqrt{g/k}$ is the group speed
in deep water.
Although the absence of wave growth and dissipation is not generally realistic
in the open ocean, it is a useful approximation here to isolate the effects
of hydrodynamic modulation solely due to the motion of the long waves.

@@

\backsection[Data availability statement]{
  The code to run the numerical simulations and generate the figures in this
  paper is available at \url{https://github.com/wavesgroup/wave-modulation-paper}.
  The numerical model is available as a standalone Python package at
  \url{https://github.com/wavesgroup/2wave}.
  %See JFM's \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/journal-policies/research-transparency}{research transparency policy} for more information
}
